The fraction of polar aligned circumbinary disks

### 2025-05-05 src/tex/ms.tex
Talk about triple systems

>>>>

\subsection{Effects of companions}
\RR{
    In this work we have only considered disks orbiting isolated binary systems, however, we can qualitatively extend our results to hierarchical triple star systems as well. There are two such cases to consider: 1) the outer-companion case where third star orbits exterior to the disk, and 2) the inner-companion case, where the disk orbits the tripe-star system. In both the outer \citep[see][]{martin2022,ceppi2023} and inner \citep[see][]{lepp2023,lepp2025} cases, additional conditions are imposed for libration to occur, and $f_\text{polar}$ decreases. The magnitude of these effects is dependent on the geometry of the triple-star system.
}
